%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Duje Vukovac} \\ \vspace{1pt}
    \small \href{mailto:x@x.com}{dvcsmail@gmail.com} $|$
    \href{https://www.linkedin.com/in/dujevukovac/}{LinkedIn} $|$
    \href{https://github.com/duje-vuk}{GitHub}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vrije Universiteit Amsterdam}{Amsterdam, NL}
      {Bachelor of Science, Computer Science}{Sep 2025 -- Sep 2028}
      \small{\textbf{Coursework}{: Data Structures and Algorithms, Smart Systems Engineering, Web Technology, Computer Programming}}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Solo Developer}{\textit{2025 -- Present}}
      {Personal Projects}{}
      \resumeItemListStart
        \resumeItem{Building AI-powered tools ranging from a Telegram bot for spaced repetition to a news aggregator with LLM-generated summaries.}
        \resumeItem{Developed a full-stack web app for startup evaluation practice using Flask, SQLite, and Groq API.}
        \resumeItem{Shipped each project end-to-end from idea to working product across Python, Node.js, Flask, Express, and SQLite.}
      \resumeItemListEnd

    \resumeSubheading
      {Head of Mod Development}{\textit{Sep 2021 -- Sep 2023}}
      {Hearts of Iron IV Community}{}
      \resumeItemListStart
        \resumeItem{Built, maintained and optimized a multisystem mod using Paradox's scripting framework, reaching hundreds of downloads.}
        \resumeItem{Achieved approximately 30\% improvement in in-game performance through mod optimization.}
    \resumeItemListEnd

    \resumeSubheading
      {Community Manager}{\textit{Sep 2021 -- Sep 2023}}
      {Hearts of Iron IV Community}{}
      \resumeItemListStart
        \resumeItem{Grew community from 30 to over 500 members, leading a team of 8 moderators.}
        \resumeItem{Organized over 50 events with over 80\% capacity fill rate and brokered partnerships yielding 2 competitive tournaments.}
        \resumeItem{Designed community advertising systems and tracked member analytics via spreadsheets.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{StudyBot} $|$ \emph{Python, Telegram API, Groq API}}{}
          \resumeItemListStart
            \resumeItem{Built a custom Telegram bot connected to Groq API that turns study materials into active recall questions.}
            \resumeItem{Supports PDF uploads, approve/reject filtering, scheduled question delivery, and weak-topic tracking.}
            \resumeItem{Generated over 130 vetted questions in one week.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Daily Briefing} $|$ \emph{Node.js, Express, Groq API, NewsAPI, Reddit API}}{}
          \resumeItemListStart
            \resumeItem{Developed an AI-powered news dashboard aggregating Reddit and NewsAPI feeds.}
            \resumeItem{Integrated Groq LLM for AI-generated summaries.}
            \resumeItem{Proxied multiple APIs through an Express backend.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Startup Evaluation Tool} $|$ \emph{Python, Flask, SQLite, Groq API, Hacker News API}}{}
          \resumeItemListStart
            \resumeItem{Built a Flask web app as a daily startup judgment trainer using Hacker News and Groq LLM.}
            \resumeItem{Fetches Show HN posts, structures startups for evaluation, then reveals AI-generated critique post-submission.}
            \resumeItem{Sessions persist in SQLite with full history tracking.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, HTML/CSS, Assembly, MATLAB} \\
     \textbf{Frameworks}{: Flask, Node.js, Express} \\
     \textbf{Developer Tools}{: Git, SQLite, Claude Code} \\
     \textbf{APIs}{: Telegram API, Groq API, NewsAPI, Reddit API, Hacker News API}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
